Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-08-24 ms_pre_post.Rmd
Write first paragraph of methods

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "May 27, 2016"
output:
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
  pdf_document:
    fig_caption: yes
  html_document: default
linestretch: 1
---

@@

******************************-

@@

>>>>

---
title: "Evolution of precopulatory and postcopulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  html_document: default
  pdf_document:
    fig_caption: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
linestretch: 1
bibliography: ms_pre_post.bib
---

@@

@@

```{r,echo=FALSE}
#**First paragraph** A general overview of what the model is doing, which will look a lot like Duthie and Reid (AmNat) and Duthie et al. (Evolution). Mention somewhere in here that all individuals have 30 diploid loci, ten with alleles affecting polyandry, ten with alleles affecting pre-copulatory inbreeding strategy, and ten with alleles affecting post-copulatory inbreeding strategy. Also note that the traits affected by each of these loci can each potentially come with some cost ($c_P$, $c_M$, and $c_F$). Note that we are not assuming any constraints on accessibility to males, so all males are available at all times.
```

We track interactions among discrete individuals in a small focal population that persists over multiple generations. Individuals within this population are either female or male, and are potentially related if they share a common ancestory. We record the coefficient of kinship ($k$), defined as the probability that a randomly selected homologous allele from each individual is identical-by-descent, between all pairs of individuals in each generation using the population pedigree [see @Boyce1983; @Duthie]. At the start of each generation, each female pays up to three independent costs of (1) tendency to engage in polyandry ($c_{P}$), (2) mating strategy with respect to inbreeding ($c_{M}$), and (3) fertilisation strategy ($c_{F}$) with respect to inbreeding. The number of males that a focal female mates with ($N_{males}$) is determined by the effects of 20 alleles ($P_{a}$) across 10 diploid loci that combine additively to determine a her genotype ($P_{g}$), and ultimately the phenotype for her tendency to engage in polandry ($P_{p}$). A focal female's choice of mate(s) is affected by 20 alleles ($M_{a}$) across 10 diploid loci that combine additively to affect her genotype ($M_{g}$) and phenotype ($M_{p}$) for pre-copulatory inbreeding avoidance or preference, and $k$ between the focal female and her potential mates. Similarly, after mating has occurred, fertilisation of a focal female's $n$ total offspring is affected by 20 alleles ($F_{a}$) across 10 diploid loci that combine additively to affect the genotype ($F_{g}$) and phenotype ($F_{p}$) of the degree to which fertilisation success is affected by $k$. After fertilisation, the vialbility of a focal female's $n$ offspring is decreased by inbreeding depression ($\beta$); surviving offspring become adults. After inbreeding depression in offspring, $\rho$ adult male immigrants arrive in the population, then density effects reduce the entire population down to female ($K_{f}$) and male ($K_{m}$) carrying capacity. Over generations, we record mean values of alleles underlying polyandry, mating strategy, and fertilisation strategy.
